\LARGE A double-sampling extension of the German National Forest Inventory for design-based small area regression estimation of timber volume resources on forest district levels \\ \vspace{2ex} \large Large scale application to the federal state of Rhineland-Palatinate \vspace{-1ex}

### 2018-02-12 Draft_Form/tab/modacc_modterms.tex
update 12_02_2018
update 12_02_2018

% latex table generated in R 3.4.2 by xtable 1.8-2 package
% Sun Jan 07 17:11:26 2018
\begin{table*}[!htbp]
	\begin{center}
	\caption{Accuracy metrics for the two OLS regression models. Interaction terms are indicated by ':'. () give the respective values on the cluster level.} 
	\label{tab:modacc_modterms}
    {\small %
	\begin{tabular}{llccc}
  \hline
model terms & model & $R^2_{adj}$ & RMSE & RMSE\% \\ 
  \hline
meanheight + stddev + meanheight$^2$ +  & full model &  0.48 & 139.22  & 45.98 \\
treespecies + ALSyear + & & (0.53) &  (101.61) & (33.57) \\ 
meanheight:treespecies + \\ meanheight:ALSyear + meanheight:stddev + \\ stddev:ALSyear &&& \\ \\

meanheight + stddev + meanheight$^2$ + & reduced model  & 0.45  & 144.13 & 47.60 \\
ALSyear + meanheight:ALSyear + & & (0.49) & (106.08) & (35.40) \\
meanheight:stddev + stddev:ALSyear &&& \\ \\
\hline
\hline
\end{tabular}
}%
\end{center}
\end{table*}
%\endgroup

>>>>

% latex table generated in R 3.4.2 by xtable 1.8-2 package
% Sun Jan 07 17:11:26 2018
\begin{table*}[!htbp]
	\begin{center}
	\caption{Accuracy metrics for the two OLS regression models on the cluster level. Interaction terms are indicated by ':'. () give the respective values on the plot level.} 
	\label{tab:modacc_modterms}
    {\small %
	\begin{tabular}{llccc}
  \hline
model terms & model & $R^2_{adj}$ & RMSE & RMSE\% \\ 
  \hline \hline
meanheight + stddev + meanheight$^2$ +  & full model &  0.59 & 101.62  & 33.57 \\
treespecies + ALSyear + & & (0.48) &  (139.22) & (45.98) \\ 
meanheight:treespecies + \\ meanheight:ALSyear + meanheight:stddev + \\ stddev:ALSyear &&& \\ \\

meanheight + stddev + meanheight$^2$ + & reduced model  & 0.56  & 106.08 & 35.4 \\
ALSyear + meanheight:ALSyear + & & (0.45) & (144.13) & (47.60) \\
meanheight:stddev + stddev:ALSyear &&& \\ \\
\hline
\hline
\end{tabular}
}%
\end{center}
\end{table*}
%\endgroup

### 2018-02-12 Draft_Form/tex/Materials_and_Methods(2).tex
update 10_02_2018
update 10_02_2018
update 12_02_2018
update 12_02_2018

% NOTES:
%
% Add Table:
% provide table of "forest characteristics" in RLP
% adress sample sizes before and after extension (table?)
%
% move this to discussion:
% It should however be mentioned that a discrepancy between the terrestrially made forest/non-forest decision and that based on the polygon stand layer can lead to missing responses in the terrestrial sample $s_2$. This occurs if a terrestrial plot $x_l \in s_2$ does not provide the terrestrial response variable although its plot center would theoretically fall within the boundaries of the stand layer. For these cases, it is important to note that according to the double sampling estimator described in Section \ref{sec:SAestimators}, the plots of a cluster can either only belong to the sample $s_2$ or $s_1$. The missing terrestrial plot information $Y(x)$ can thus not be replaced by a prediction $\hat{Y}(x)$, i.e. by establishing a plot $x \in s_1$ instead, and has thus to be treated as a non-response.\par
%
%  "This extension led to a considerable increase of the sample size $n_{1,G}$ in the small area units of both, the FA and FR level."
% - Show (theoretical) increase in sample sizes by extension to 2phase scheme 
%   --> these sample sizes are in the following reduced by missing rs-info
%
% - Add Graphik showing RLP, zoom into 3 management levels including 2-phase sample
%   (big graphic, can take 1/2 page later)

@@

% Graphik:
\begin{figure}[H]
	\centering
	\resizebox{0.9\hsize}{!}{\includegraphics*{fig/AuxvarsLOWRES.png}}
	\caption{Left: CHM (top) and tree species classification map (bottom) available on the federal state level were used as auxiliary information. Right: Magnified illustration of the supports used to derive the explanatory variables from the auxiliary data.}
	\label{fig:Auxvars}
\end{figure}

@@

\begin{table}[H]
	\begin{center}
		\caption{Classification accuracies of the \textit{treespecies} variable before and after calibration. $n_{ref}$: number of terrestrial reference plots. $n_{class}$: number of classified plots.}
		\vspace{0.2cm}
		\label{tab:classacc}
		{\small %
			\begin{tabular}{l|c|c|c|c} %8cols
				\hlineB{1}
				Main plot species & Producer's accuracy[\%] & User's accuracy[\%] & nref & nclass \\
				\hline \hline	
				Beech       & 22.31 & 47.02 & 883 & 419 \\
				Douglas Fir & 24.78 & 48.72 & 230 & 117 \\
				Oak         & 11.07 & 48.48 & 289 & 66 \\
				Spruce      & 53.15 & 61.13 & 651 & 566 \\
				Scots Pine  & 22.91 & 46.07 & 179 & 89 \\
				Mixed       & 84.49 & 64.53 & 3152 & 4127 \\
				\hline
				& \multicolumn{2}{l|}{Overall accuracy: 61.96\%} & 5384 & 5384 \\
				\hline \hline
			\end{tabular}
		}%
	\end{center}
\end{table}

%\begin{table}[H]
%	\begin{center}
%	\caption{Classification accuracies of the \textit{treespecies} variable before and after calibration. $n_{ref}$: number of terrestrial reference plots. $n_{class}$: number of classified plots.}
%	\vspace{0.2cm}
%	\label{tab:classacc}
% {\small %
%	\begin{tabular}{l|c c|c c|c|c c} %8cols
%		\hlineB{1}
%		\multirow{2}{*}{Main plot species} & \multicolumn{2}{c|}{Producer's accuracy[\%]} & \multicolumn{2}{c|}{User's accuracy[\%]} & \multirow{2}{*}{nref} & \multicolumn{2}{c}{nclass} \\ 
%		\cline{2-3} \cline{4-5} \cline{7-8} & uncalib & calib & uncalib & calib & & uncalib & calib \\
%		\hline \hline	
%		 Beech       & 29.56 & 22.31 & 46.11 & 47.02 & 883 & 566 & 419 \\
%		 Douglas Fir & 33.04 & 24.78 & 47.50 & 48.72 & 230 & 160 & 117 \\
%		 Oak         & 47.75 & 11.07 & 24.34 & 48.48 & 289 & 567 & 66 \\
%		 Spruce      & 43.63 & 53.15 & 60.81 & 61.13 & 651 & 467 & 566 \\
%		 Scots Pine  & 55.87 & 22.91 & 29.59 & 46.07 & 179 & 338 & 89 \\
%		 Mixed       & 66.40 & 84.49 & 63.69 & 64.53 & 3152 & 3286 & 4127 \\
%		\hline
%		 & \multicolumn{4}{l|}{Overall accuracy: 54.83\% (61.96\%)} & 5384 & \multicolumn{2}{c}{5384} \\
%		 \hline \hline
%	\end{tabular}
%}%
%	\end{center}
%\end{table}

@@

The model with highest \adjrsq{} and lowest RMSE was achieved with the variables \meanheight{}, \meanheight{}$^2$, \stddev{} and \alsyear{} derived from the ALS data as well as the \treespecies{} variable derived from the classification map as main effect terms. Additionally, interaction terms between \meanheight{} and \alsyear{}, \stddev{} and \alsyear{}, \meanheight{} and \stddev{}, and \meanheight{} and \treespecies{} were included. The model yielded an \adjrsq{} of 0.48 and an RMSE of 140.62 \mha{} (46.7\%) on the plot level (table \ref{tab:modacc_modterms}, full model). While the study of \citet{hill2017a} only provide the model evaluations on the plot level, the two-phase estimators described in section \ref{sec:SAestimators} derive and apply the regression coefficients and the residuals on the aggregated cluster level. We thus re-evaluated the model as used in the estimators also on the cluster level and found the model accuracies to be higher than on the plot level (\adjrsq{} of 0.53 and RMSE of 101.61 \mha{} and 33.6\%). A stratification to the ALS acquisition years substantially improved the model accuracy and thus proved to be an effective means in accounting for the artificially introduced noise in the data set due to ALS quality variations and time-gaps between the ALS and the terrestrial survey. However, the stratification led to a highly unbalanced dataset when stratifying according to the \treespecies{} variable. For this reason, a species individual modeling within each \alsyear{} stratum remained infeasible, but might have further improved the model accuracy. An additional evaluation of the model residuals within each ALS acquisition year stratum revealed that the model accuracies substantially varied between the strata (table \ref{tab:adj_r2_within}). Values above the overall \adjrsq{} were particularly achieved in ALS acquisition years close to the terrestrial survey date (0.59 to 0.66 on the cluster level). This effect was substantially diminished when dropping the \alsyear{} variable from the model term.\par

@@

@@

%We conducted an Influence Analysis, i.e. leverage / outlier detection, for the 'final model'. We here considered the usually applied criteria of \textit{Leverages} and \textit{Cook's Distance} as amongst others described in Fahrmeir 2013 \{Regression: models, methods and applications. \textit{Springer Science \& Business Media}. page 164-167\}. The critical threshold of $2p/n$ (i.e. twice the average of the hat matrix' diagonal entries), was exceeded by 10\% of the observations. However, only 3\% of these leverage points were assigned to studentized residuals > 1 or < -1. Leaving these 3\% of points out and recalculating the final model lead to a $R^{2}_{adj}$ of 0.494 compared to 0.485 when including them in the regression. The Cook's Distance values $D_i$ did not exceed a value of 0.019, and thus were far apart from the often cited critical threshold of $D_i > 0.5$. Based on these findings, we decided not to remove observations from the modelling data set. We added a paragraph commenting on this issue of influential data points in section 3.3 'Final Regression Model', page 9 RHS line 690-707.

>>>>

% NOTES:
%
% Add Table:
% provide table of "forest characteristics" in RLP
% adress sample sizes before and after extension (table?)
%
% move this to discussion:
% It should however be mentioned that a discrepancy between the terrestrially made forest/non-forest decision and that based on the polygon stand layer can lead to missing responses in the terrestrial sample $s_2$. This occurs if a terrestrial plot $x_l \in s_2$ does not provide the terrestrial response variable although its plot center would theoretically fall within the boundaries of the stand layer. For these cases, it is important to note that according to the double sampling estimator described in Section \ref{sec:SAestimators}, the plots of a cluster can either only belong to the sample $s_2$ or $s_1$. The missing terrestrial plot information $Y(x)$ can thus not be replaced by a prediction $\hat{Y}(x)$, i.e. by establishing a plot $x \in s_1$ instead, and has thus to be treated as a non-response.\par
%
%  "This extension led to a considerable increase of the sample size $n_{1,G}$ in the small area units of both, the FA and FR level."
% - Show (theoretical) increase in sample sizes by extension to 2phase scheme 
%   --> these sample sizes are in the following reduced by missing rs-info
%

@@

% Graphik:
\begin{figure}[H]
	\centering
	\resizebox{0.9\hsize}{!}{\includegraphics*{fig/Auxvars_100dpi.png}}
	\caption{Left: CHM (top) and tree species classification map (bottom) available on the federal state level were used as auxiliary information. Right: Magnified illustration of the supports used to derive the explanatory variables from the auxiliary data.}
	\label{fig:Auxvars}
\end{figure}

@@

\begin{table}[H]
	\begin{center}
		\caption{Classification accuracies of the \textit{treespecies} variable before and after calibration. $n_{ref}$: number of terrestrial reference plots. $n_{class}$: number of classified plots.}
		\vspace{0.2cm}
		\label{tab:classacc}
		{\small %
			\begin{tabular}{l|c|c|c|c} %8cols
				\hline
				Main plot species & Producer's accuracy[\%] & User's accuracy[\%] & nref & nclass \\
				\hline \hline	
				Beech       & 22.31 & 47.02 & 883 & 419 \\
				Douglas Fir & 24.78 & 48.72 & 230 & 117 \\
				Oak         & 11.07 & 48.48 & 289 & 66 \\
				Spruce      & 53.15 & 61.13 & 651 & 566 \\
				Scots Pine  & 22.91 & 46.07 & 179 & 89 \\
				Mixed       & 84.49 & 64.53 & 3152 & 4127 \\
				\hlineB{2}
				& \multicolumn{2}{l|}{Overall accuracy: 61.96\%} & 5384 & 5384 \\
				\hline \hline
			\end{tabular}
		}%
	\end{center}
\end{table}

%% Here is the table with calibrated and uncalibrated values:
%\begin{table}[H]
%	\begin{center}
%	\caption{Classification accuracies of the \textit{treespecies} variable before and after calibration. $n_{ref}$: number of terrestrial reference plots. $n_{class}$: number of classified plots.}
%	\vspace{0.2cm}
%	\label{tab:classacc}
% {\small %
%	\begin{tabular}{l|c c|c c|c|c c} %8cols
%		\hlineB{1}
%		\multirow{2}{*}{Main plot species} & \multicolumn{2}{c|}{Producer's accuracy[\%]} & \multicolumn{2}{c|}{User's accuracy[\%]} & \multirow{2}{*}{nref} & \multicolumn{2}{c}{nclass} \\ 
%		\cline{2-3} \cline{4-5} \cline{7-8} & uncalib & calib & uncalib & calib & & uncalib & calib \\
%		\hline \hline	
%		 Beech       & 29.56 & 22.31 & 46.11 & 47.02 & 883 & 566 & 419 \\
%		 Douglas Fir & 33.04 & 24.78 & 47.50 & 48.72 & 230 & 160 & 117 \\
%		 Oak         & 47.75 & 11.07 & 24.34 & 48.48 & 289 & 567 & 66 \\
%		 Spruce      & 43.63 & 53.15 & 60.81 & 61.13 & 651 & 467 & 566 \\
%		 Scots Pine  & 55.87 & 22.91 & 29.59 & 46.07 & 179 & 338 & 89 \\
%		 Mixed       & 66.40 & 84.49 & 63.69 & 64.53 & 3152 & 3286 & 4127 \\
%		\hline
%		 & \multicolumn{4}{l|}{Overall accuracy: 54.83\% (61.96\%)} & 5384 & \multicolumn{2}{c}{5384} \\
%		 \hline \hline
%	\end{tabular}
%}%
%	\end{center}
%\end{table}

@@

The model with highest \adjrsq{} and lowest RMSE was achieved with the variables \meanheight{}, \meanheight{}$^2$, \stddev{} and \alsyear{} derived from the ALS data as well as the \treespecies{} variable derived from the classification map as main effect terms. Additionally, interaction terms between \meanheight{} and \alsyear{}, \stddev{} and \alsyear{}, \meanheight{} and \stddev{}, and \meanheight{} and \treespecies{} were included. The model yielded an \adjrsq{} of 0.48 and an RMSE of 140.62 \mha{} (46.7\%) on the plot level (table \ref{tab:modacc_modterms}, full model). While the study of \citet{hill2017a} only provide the model evaluations on the plot level, the two-phase estimators described in section \ref{sec:SAestimators} derive and apply the regression coefficients and the residuals on the aggregated cluster level. We thus re-evaluated the model as used in the estimators also on the cluster level and found the model accuracies to be higher than on the plot level (\adjrsq{} of 0.59 and RMSE of 101.61 \mha{} and 33.6\%). A stratification to the ALS acquisition years substantially improved the model accuracy and thus proved to be an effective means in accounting for the artificially introduced noise in the data set due to ALS quality variations and time-gaps between the ALS and the terrestrial survey. However, the stratification led to a highly unbalanced dataset when stratifying according to the \treespecies{} variable. For this reason, a species individual modeling within each \alsyear{} stratum remained infeasible, but might have further improved the model accuracy. An additional evaluation of the model residuals within each ALS acquisition year stratum revealed that the model accuracies substantially varied between the strata (table \ref{tab:adj_r2_within}). Values above the overall \adjrsq{} were particularly achieved in ALS acquisition years close to the terrestrial survey date (0.60 to 0.65 on the cluster level). This effect was substantially diminished when dropping the \alsyear{} variable from the model term.\par

@@

%\begin{equation}\label{eq:R_squared_clust}
%R^2 =  \frac{\sum_{x \in s_2} \Big(\frac{M(x)}{\bar{M_2}}\Big)^2 \Big(\hat{Y}_{c}(x)-\bar{Y}_c(x)\Big)^2}{\sum_{x \in s_2} \Big(\frac{M(x)}{\bar{M_2}}\Big)^2 \Big(Y_{c}(x)-\bar{Y}_c(x)\Big)^2}
%\end{equation}

@@
